Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-02-13 vesicle_code/docs/adhesion/adhesion.tex
minor changes at the end of conclusion by yny
small changes

In Figure~\ref{fig:extensionalInclinationAngle}, we plot the inclination
angle of the doublet as a function of time for four different
extensional rates (left) and the final inclination angle for all
doublets that reach an equilibrium state (middle).  We observe that not
only do smaller extensional rates result in smaller inclination
angles, but smaller reduced areas also result in smaller inclination
angles.  
%
%From physics we expect that stronger adhesion is required to keep 
%the vesicle doublet intact under a fluid trap as we increase the flow rate.
%
%It is less obvious how the critical adhesion strength depends on the reduced area of the vesicles.
%
%Even though we only used one value of Hamaker constant (${\cal H} = 0.7$) we expect that
%
%Moreover, the critical Hamaker constant that determines if the
%doublet remains trapped or is broken decreases with an increasing
%extensional rate \todo[inline]{not sure how we can say this since we've
%only considered one Hamaker constant}.  
%
We summarize the final
inclination angle of the doublet in the right plot of
Figure~\ref{fig:extensionalInclinationAngle}.  
The size of the round
dots are scaled to the final inclination angle as defined in
Figure~\ref{fig:InclinationAngle}.  At smaller extensional rates, the
vesicles come closer to aligning their long axis with the diverging
direction.  When the doublet is broken at reduced area $\Delta A =
0.80$, the extensional rate is sufficiently large to align the long axis
of the vesicle with the diverging direction and then the vesicles
separate (Figure~\ref{fig:extensional3}).  For very low extensional
rates, the time horizon is insufficient for the doublet to reach an
equilibrium state, and these simulations are marked with a square.  The
right plot of Figure~\ref{fig:extensionalInclinationAngle} also
summarizes the reduced areas and extensional rates that result in a
bound vesicle doublet in a fluid trap: Parameter values with a blue mark
result in a fluid trap and parameter values with a red mark result in
vesicle separation.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions\label{sec:conclusions}}
In this work we use boundary integral formulation with adaptive
time-stepping to simulate hydrodynamics of two vesicles with adhesive
interactions.  In a quiescent flow, two vesicles that are initially
sufficiently far apart move towards each other under a long-range
attraction.  We use a lubrication theory to estimate the time required
to reach the separation distance $\delta$, and the theoretical scaling
is in good agreement with numerical results.  Once two membranes are
within separation distance $\delta$, the adhesive force turns repulsive
and the membranes flatten to form a contact region.  Our simulations
show that the membranes in the contact region are actually curved with
end points at the shortest distance.  Once a vesicle doublet forms, we
examine the dependence of membrane bending and adhesion energies on the
reduced area, the Hamaker constant, and the separation distance.

@@

In our formulation we did not include any electrostatic interactions
between membranes under adhesion. When the electrostatic interaction is
important, an electro-osmotic pressure in the thin film is found to be
responsible for the observed membrane
undulation~\cite{SteinkuhlerAgudo-Canalejo2016_BJ}.  In addition,
simulations presented in this work are for identical vesicles (same
reduced area, length, and bending rigidity modulus) in the doublet.
Flormann {\it et al.} demonstrated that asymmetric vesicle reduced area
may lead to various equilibrium doublet shape such as male-female,
asymmetric S-shape, and parachute shape.  It is also possible that
viscosity contrast may also lead to different equilibrium doublet
shapes.  Future work includes three dimensional simulations, dispersive
vesicle properties (such as reduced area and bending modulus), viscosity
contrast, and effects of confinement on adhesive interactions.

Flormann {\it et al.} studied the clustering and packing of vesicles in
free suspension~\cite{FlormannAouane2017_SciReports}.  In engineering
applications of vesicle emulsions, smaller vesicles are often enclosed in
a big vesicle, as shown in Figure~\ref{fig:relaxationManyVes}, where
the left panel shows an initial condition of five vesicles suspended
inside of a larger vesicle.  The second panel from the left shows the
membrane configuration and flow streamlines at an intermediate time.
There is no imposed flow, so the dynamics is governed entirely by the
vesicle forces, including adhesion.  In the absence of confinement,
we would expect the vesicles to align themselves as a rouleaux with the
membranes forming a parachute, male-female, or S-shape
configuration~\cite{FlormannAouane2017_SciReports}.  However, because of
the bounding vesicle and the dense packing, the interior vesicles align
themselves differently.  
The bounding membrane evolves dynamically together with all the interior 
vesicles to minimize the total membrane energy.
%In addition, several parts of the bounding
%membrane closely follow the interior membranes in order to minimize the
%adhesion energy.   
%

@@

Finally, it is not clear how thermal fluctuations may affect the
hydrodynamics of vesicles under adhesion. For example, does the
fluctuating hydrodynamics in the thin film between two vesicles enhance
adhesion to keep vesicles bound under linear flows?
Recently Liu {\em et al.}~\cite{LiuChuNewbyRead2018_bioRxiv} used
immersed boundary simulations to show that, at a separation distance of
tens of nanometers, the thin film between the two membranes facilitate
the coupling between membranes via strong hydrodynamic interactions. In
particular, they demonstrate numerically that the fluctuation in one
membrane is highly correlated to the other membrane without any physical
contact. We are actively pursuing this direction with ongoing modeling and simulations
of adhesive membranes with fluctuating hydrodynamics.

>>>>

In Figure~\ref{fig:extensionalInclinationAngle}, we plot the inclination
angle of the doublet as a function of time for four different
extensional rates (left) and the final inclination angle for all
doublets that reach an equilibrium state (middle).  We observe that not
only do smaller extensional rates result in smaller inclination angles,
but smaller reduced areas also result in smaller inclination angles.  We
summarize the final inclination angle of the doublet in the right plot
of Figure~\ref{fig:extensionalInclinationAngle}.  The size of the round
dots are scaled to the final inclination angle as defined in
Figure~\ref{fig:InclinationAngle}.  At smaller extensional rates, the
vesicles come closer to aligning their long axis with the diverging
direction.  When the doublet is broken at reduced area $\Delta A =
0.80$, the extensional rate is sufficiently large to align the long axis
of the vesicle with the diverging direction and then the vesicles
separate (Figure~\ref{fig:extensional3}).  For very low extensional
rates, the time horizon is insufficient for the doublet to reach an
equilibrium state, and these simulations are marked with a square.  The
right plot of Figure~\ref{fig:extensionalInclinationAngle} also
summarizes the reduced areas and extensional rates that result in a
bound vesicle doublet in a fluid trap: Parameter values with a blue mark
result in a fluid trap and parameter values with a red mark result in
vesicle separation.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions\label{sec:conclusions}}
In this work we use a boundary integral formulation with adaptive
time-stepping to simulate hydrodynamics of two vesicles with adhesive
interactions.  In a quiescent flow, two vesicles that are initially
sufficiently far apart move towards each other under a long-range
attraction.  We use a lubrication theory to estimate the time required
to reach the separation distance $\delta$, and the theoretical scaling
is in good agreement with numerical results.  Once two membranes are
within separation distance $\delta$, the adhesive force turns repulsive
and the membranes flatten to form a contact region.  Our simulations
show that the membranes in the contact region are actually curved with
end points at the shortest distance.  Once a vesicle doublet forms, we
examine the dependence of membrane bending and adhesion energies on the
reduced area, the Hamaker constant, and the separation distance.

@@

In our formulation we did not include any electrostatic interactions
between membranes under adhesion. When the electrostatic interaction is
important, an electro-osmotic pressure in the thin film is found to be
responsible for the observed membrane
undulation~\cite{SteinkuhlerAgudo-Canalejo2016_BJ}.  In addition,
simulations presented in this work are for identical vesicles (same
reduced area, length, and bending rigidity modulus) in the doublet.
Flormann {\em et al.}~demonstrated that asymmetric vesicle reduced area
may lead to various equilibrium doublet shape such as male-female,
asymmetric S-shape, and parachute shape.  It is also possible that
viscosity contrast may also lead to different equilibrium doublet
shapes.  Future work includes three dimensional simulations, dispersive
vesicle properties (such as reduced area and bending modulus), viscosity
contrast, and effects of confinement on adhesive interactions.

Flormann {\it et al.} studied the clustering and packing of an
unbounded suspension of vesicles~\cite{FlormannAouane2017_SciReports}.  In engineering
applications of vesicle emulsions, smaller vesicles are often enclosed in
a big vesicle, as shown in Figure~\ref{fig:relaxationManyVes}, where
the left panel shows an initial condition of five vesicles suspended
inside of a larger vesicle.  The second panel from the left shows the
membrane configuration and flow streamlines at an intermediate time.
There is no imposed flow, so the dynamics is governed entirely by the
vesicle forces, including adhesion.  In the absence of confinement, we
would expect the vesicles to align themselves as a rouleaux with the
membranes forming a parachute, male-female, or S-shape
configuration~\cite{FlormannAouane2017_SciReports}.  However, because of
the bounding vesicle and the dense packing, the interior vesicles align
themselves differently.  The bounding membrane evolves dynamically
together with all the interior vesicles to minimize the total membrane
energy.

@@

Finally, it is not clear how thermal fluctuations may affect the
hydrodynamics of vesicles under adhesion. For example, does the
fluctuating hydrodynamics in the thin film between two vesicles enhance
adhesion to keep vesicles bound under linear flows?  Recently Liu {\em
et al.}~\cite{LiuChuNewbyRead2018_bioRxiv} used immersed boundary
simulations to show that, at a separation distance of tens of
nanometers, the thin film between the two membranes facilitate the
coupling between membranes via strong hydrodynamic interactions. In
particular, they demonstrate numerically that the fluctuation in one
membrane is highly correlated to the other membrane without any physical
contact. We are actively pursuing this direction with hydrodynamic
modeling and simulations of adhesive membranes with thermal fluctions.
